---
title: "Exercise_3"
author: "Mathujah Manikkan"
date: "5/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages 
```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(SimilarityMeasures)
library(tidyr)
```

## Implement file(s)
```{r warning=FALSE}
caro <- read_delim("caro60.csv")

```


# Task 1: Segmentation
## Step a): Specify a temporal window v
### The sampling interval for this dataset is 1 minute. Use a temporal window v of 6 minutes, i.e. a window size of 6 positions (n±3).

1. pos[n-3] to pos[n]
2. pos[n-2] to pos[n]
3. pos[n-1] to pos[n]
4. pos[n] to pos[n+1]
5. pos[n] to pos[n+2]
6. pos[n] to pos[n+3]

## Step b): Measure the distance from every point to every other point within this temporal window v
 
```{r warning=FALSE}
caro <- caro %>%
  mutate(
    nMinus3 = sqrt((lag(E,3)-E)^2+(lag(N,3)-N)^2),   # distance to pos -3 minutes
    nMinus2 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2),   # distance to pos -2 minutes
    nMinus1 = sqrt((lag(E,1)-E)^2+(lag(N,1)-N)^2),   # distance to pos -1 minute
    nPlus1  = sqrt((E-lead(E,1))^2+(N-lead(N,1))^2), # distance to pos +1 mintue
    nPlus2  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2), # distance to pos +2 minutes
    nPlus3  = sqrt((E-lead(E,3))^2+(N-lead(N,3))^2)  # distance to pos +3 minutes
  )

```

### Calculation the mean distance nMinus3, nMinus2, nMinus1, nPlus1, nPlus2, nPlus3
```{r warning=FALSE}
caro <- caro %>%
  rowwise() %>%
  mutate(
    stepMean = mean(c(nMinus3, nMinus2, nMinus1, nPlus1,nPlus2, nPlus3))
  ) %>%
  ungroup() 

caro

```


# Task 2: Specify and apply threshold d
```{r warning=FALSE}
hist(caro$stepMean)
boxplot(caro$stepMean)
summary(caro$stepMean)

caro <- caro %>% 
  ungroup() %>%
  mutate(static = stepMean < mean(stepMean, na.rm = TRUE))


caro_filter <- caro %>%
  filter(!static)

caro_filter%>%
  ggplot(aes(E, N))  +
  geom_path() +
  geom_point() +
  coord_fixed() +
  theme(legend.position = "bottom")

```
## Task 3: Visualize segmented trajectories
```{r warning=FALSE}

ggplot(caro, aes(E, N, colour = static)) +
  geom_path()+
  geom_point() +
  coord_equal()

```
## Task 4: Segment-based analysis

```{r warning=FALSE}

rle_id <- function(vec){
  x <- rle(vec)$lengths
  as.factor(rep(seq_along(x), times=x))
  }

caro60 <- caro %>%
  mutate(segment_id = rle_id(static))
  
caro2 <- caro60 %>%
  mutate(segment_id = rle_id(static))%>%
  filter(!static) %>%
  group_by(segment_id) %>%
  mutate(duration = n()) %>%
  filter(duration>5)


caro2

```


### Moving segments coloured by segment ID

```{r warning=FALSE}
ggplot(caro60, aes(E, N, colour = segment_id)) +
  theme(legend.position="none")+       
  geom_path()+
  geom_point() +
  coord_equal()+
  labs(title = "All segments (uncleaned)")

ggplot(caro2, aes(E, N, colour = segment_id)) +
  theme(legend.position="none")+   
  geom_path()+
  geom_point() +
  coord_equal()+
  labs(title = "Long segments (removed segements <5)")
```
# Task 5: Similarity measures
```{r warning=FALSE}
pedestrian <- read_delim("pedestrian.csv")

ggplot(pedestrian, aes(N,E, col = as.factor(TrajID)))+
  geom_point() +
  geom_path() +
  facet_wrap(~TrajID) +
  labs(title = "Visual comparison of the 6 trajectories")


```

# Task 6: Calculate similarity


